---
title: "Digital methods in urban studies"
author: "Alexander Sheludkov"
date: "18 04 2018"
output:
  html_document:
    toc: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Only Practice, Only Hardcore! During the workshop we will learn what spatial data really is, and how one creates it. You will get familiar with the basic concepts, such as coordinate system and projection, vector and raster data, points, lines, polygons, grids, shape- and geojson files. Together we will study open sources of spatial data; learn popular desktop tools and web-cartography instruments. A case study will be dedicated to urban morphology of Perm. We will study form and spatial structure of the city, revealing history of its formation and spatial growth.  
  
***

**Required software**:  
1. R <https://cran.r-project.org/>  
+ Rstudio <https://www.rstudio.com/products/rstudio/download/#download>    
+ packages
```{r install_packages, results="hide", message=FALSE}
source("Istall_required_packages.R")
```
2) QGIS <https://www.qgis.org/> (2.18, not 3.0)  
+ QuickMapServices module  
3) SelectorGadget (browser tool) <http://selectorgadget.com>

***