---
title: "Digital methods in urban studies. Part 2"
author: "Alexander Sheludkov"
date: "18 04 2018"
output: 
  html_document:
    toc: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r install_packages, message=FALSE, include=FALSE, results="hide"}
source("Istall_required_packages.R")
```


## Part 2. Data mining. Geocoding

### 2.1. Data mining

**Algorithm**:  
*Scrap data from web-pages
*Geocoding (find lon/lat coordinates)

#### 2.1.1. Load heritage data

Load data drom csv file. You can find original code in heritage.R

```{r heritage, message=FALSE, include=TRUE}
heritage_geocoded <- read_csv("data/heritage_geocoded.csv")
head(heritage_geocoded)
```

#### 2.1.2. Web scraping

**client-server model** - **HTML-file structure** - **SelectorGadget** - **pagination**

```{r scrapping reformagkh, eval=FALSE, include=TRUE}
res <- data_frame()
for(i in 1:68){
  # Follow the progress
  print(i)
  
  url <- paste0("https://www.reformagkh.ru/myhouse?tid=2299765&sort=name&order=asc&page=", i, "&limit=100")
  # Save as html page
  page <- read_html(url)
  # Extrcat address data
  page %>% 
    html_nodes('td a') %>%  # use css selector 
    html_text() -> address
  # Extract year
  page %>%
    html_nodes('.grid td:nth-child(2)') %>% 
    html_text() -> year
  res <- bind_rows(res,data_frame(address, year))
  Sys.sleep(1)
}

# Replace "н.д." with NA and change year type to integer
res %>% 
  mutate(year = str_replace(year, "н.д.", NA_character_) %>% as.integer()) -> res

# Let's take a look at the data
summary(res) # there are some stranges
res %>% arrange(year) %>% head()
# Clean the data
res[res$address == "г. Пермь, ул. Холмогорская, д. 4/2", 2] <- 1975
res[res$address == "г. Пермь, ул. Серпуховская, д. 15", 2] <- 1955
# Remove all NA rows
res %>% filter(!is.na(year)) -> res
```

Let's take a look of the results
```{r reformagkh data head, message=FALSE, warning=FALSE, include=TRUE}
res <- read_csv("data/res.csv")
head(res)
```

Check the distribution of the "year" 
```{r reformagkh data distribution, include=TRUE}
res %>% ggplot(aes(year))+
  geom_histogram(binwidth = 2)+
  labs(y = "Number of buildings", x = "Year")+
  scale_x_continuous(breaks = seq(1850, 2017, 10))
```

***

### 2.2. Geocoding


```{r geocoding, eval=FALSE, include=TRUE}
# Resulting data.frame
perm_buildings <- data_frame()

# Loop with requests to Yandex Geocoder
for (n in 1:nrow(res)) {
  # the progress
  print(n)
  # Specifying the url for desired website to be scrapped
  url <- paste0("https://geocode-maps.yandex.ru/1.x/?geocode=", res[n, 1])
  # Reading the HTML code from the website
  page <- read_html(url)
  
  # Parcing with css selector number of found results and their precision
  page %>% html_nodes('found') %>% html_text() %>% as.integer(.) -> found
  page %>% html_nodes('precision') %>% html_text() -> precision
  
  # If there are results and precision is exact, we add coords to our table
  if (found >= 1 && precision[1] == "exact") {
    coords <- page %>% html_nodes('pos') %>% html_text() %>% .[1]
    temp_table <- bind_cols(res[n,], coords = coords)
  } else {
    temp_table <- cbind(res[n,], coords = NA)
  }
  perm_buildings <- bind_rows(perm_buildings, temp_table)
  # Sleep
  Sys.sleep(1)
}

# Split coords column into Lat and Lon
perm_buildings_geocoded <- separate(perm_buildings,
                                    coords, # column to be splitted
                                    into = c("Lon", "Lat"), # new columns' names
                                    sep = " ", # separator
                                    remove = TRUE, # remove splitted column
                                    convert = TRUE) # default type conversion
# Check the results
perm_buildings_geocoded %>% summary()
# Remove NAs
perm_buildings_geocoded %>% 
  filter(!is.na(Lon)) -> perm_buildings_geocoded

# Add date_label column
perm_buildings_geocoded %>% mutate(date_label = year) -> perm_buildings_geocoded

# Add heritage data
perm_buildings_geocoded %>% rbind(., heritage_geocoded) -> perm_buildings_geocoded

# Save the results in csv file
write_csv(perm_buildings_geocoded, "data/perm_buildings_geocoded.csv")
```

Take a look at the results
```{r geocoded table, message=FALSE, warning=FALSE, include=TRUE}
perm_buildings_geocoded <- read_csv("data/perm_buildings_geocoded.csv")
nrow(perm_buildings_geocoded)
head(perm_buildings_geocoded)
```

