---
title: "Digital methods in urban studies. Part 3"
author: "Alexander Sheludkov"
date: "18 04 2018"
output:
  html_document:
    toc: true
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r install_packages, message=FALSE, include=FALSE, results="hide"}
source("Istall_required_packages.R")
```

## Part 3. Spatial data manipulation and analysis

**Algorithm**:  
*Create SpatailPoints object 
*Load OpenStreetMap data
*Assign to OSM polygons data from points 

### 3.1. Creating vector layer from csv 

This is where we start using **QGIS**.  
  
*Load csv file*:  

**Layers -> Add layer -> add CSV (pick perm-buildings-geocoded.csv)**  

Choose CRS (Coordinate Reference System): **WGS84 (EPSG:4326)**  

Now we have real spatial object! To see the attributes, click on table image in the menu.  

*To save the file*:  

**Right-click on layer in Layers Panel -> Save As -> Choose “GeoJSON” and give the name (“points”)**

***

### 3.2. Load OpenStreetMap data  

**OpenStreetMap**  

Go to <http://overpass-turbo.eu> -> Search for Perm location (define bounding box)

**Open Query Wizard -> "building" -> build query -> Run**

**Export -> Download as GeoJSON**

Copy file to your "data" directory and open in QGIS (only polygon layer):

**Layers -> Add layer -> Add vector layer -> choose the file**  
  
Since, we do not need all the attribute information from OSM, just delete it (keep only ID column):

**Right-click on layer in Layers Panel -> Properties -> Fields -> Change -> Choose and delete the fields**  
  
Save the file:  

**Right-click on layer in Layers Panel -> Save As -> Choose “GeoJSON” and give the name (“polygons”)**

***

### 3.3. Load OpenStreetMap data  

Now we need to match the data from the point and polygonal layers. If a point overlaps a polygon, we assign the data from the point to this polygon.  
Switch to R  

```{r read sp data, echo=TRUE, message=FALSE, warning=FALSE}
# Read spatial data
points <- readOGR("data/points.geojson")     # geocoded points
polygons <- readOGR("data/polygons.geojson") # osm polygons
```

Take a look at them
```{r sp data overview, echo=TRUE, message=FALSE}
points
polygons
```

We can see class, the number of features (points or polygons), CRS and summary of the data  
  
To access SpatialObjects* data use @  
  
To extract data from the overlapping objects use `over()`

```{r over, echo=TRUE, eval=FALSE}
points_data <- over(polygons, 
                    points[,c("address", "year", "date_label")])
```

The resulting data.frame has the same number of observations as the number of features in polygon layer
```{r points_data nrow, echo=TRUE, eval=FALSE}
points_data %>% nrow()
```

Now we can just assign data from `points_data` to `polygons@data` column by column

```{r polygons data, echo=TRUE, message=FALSE, eval=FALSE}
# Create new 
polygons@data$year <- points_data$year
polygons@data$address <- points_data$address
polygons@data$datelabel <- points_data$date_label
polygons@data %>% select(address, year, datelabel) -> polygons@data
```

Remove buildings with no data
```{r remove NA buildings, echo=TRUE, message=FALSE, eval=FALSE}
# Remove buildings with NA year
perm_buildings_osm_year <- polygons[!is.na(polygons@data$year), ]
```

There only 4509 features left  

Save the polygon layer as new GeoJSON file
```{r save file, echo=TRUE, message=FALSE, eval=FALSE}
writeOGR(obj = perm_buildings_osm_year, dsn = "data/perm_buildings_age.geojson", 
         layer = "perm_buildings_age.geojson", driver = "GeoJSON", overwrite_layer = T)
```



